### 2024-11-26 paper/al.tex
Fix model explanation

SpecTec introduces AL, an algorithmic specification language, for specifying
the prose specification.
Since the prose notation of the official specification is informal, it is
essential to rigorously define AL to ensure an correct specification, rather
than merely imitating the original.
We begin by outlining the informality of the prose specification in
\cref{sec:prose-informal}.
Next, we propose a formal model for Wasm control flow in AL in
\cref{sec:model}.
We then define the syntax and the semantics of AL in \cref{sec:definition}.
Finally, we produce an executable Wasm specification using AL interpreter that
ensures the correctness of the specification in \cref{sec:exec-spec}.

@@

% TODO: Clever way to distinguish jargon rather then \textit
% Formal model
To formally specify the prose specification, we construct a formal model to
describe Wasm control flow.
% Execute
Rather than relying on a program counter, we employ an instruction stack to
represent execution progress.
Execution proceeds by popping an instruction from the stack and performing its
operation.
To avoid confusion with the stack that contains values interleaved with
contexts, we refer to the latter as the \textit{interleaved stack}.
This approach allows us to define the execute operation without introducing a
program counter.

>>>>

SpecTec introduces AL, an algorithmic specification language, for specifying
the prose specification.
Since the prose notation of the official specification is informal, it is
essential to rigorously define AL to ensure an correct specification, rather
than merely imitating the original.
We begin by outlining the informality of the prose specification in
\cref{sec:prose-informal}.
Next, we propose a formal model for the prose specification \cref{sec:model}.
We then define the syntax and the semantics of AL in \cref{sec:definition}.
Finally, we produce an executable Wasm specification using AL interpreter that
ensures the correctness of the specification in \cref{sec:exec-spec}.

@@

% TODO: Clever way to distinguish jargon rather then \textit
% Formal model
To formally specify the prose specification, we construct a formal model the
prose specification.
% Execute
Rather than relying on a program counter, we employ an instruction stack to
represent execution progress.
Execution proceeds by popping an instruction from the stack and performing its
operation.
To avoid confusion with the stack that contains values interleaved with
contexts, we refer to the latter as the \textit{interleaved stack}.
This approach allows us to define the execute operation without introducing a
program counter.

### 2024-11-26 paper/intro.tex
Fix model explanation

% Solution
To address this, we present a formal model for how AL describes Wasm control
flow.
Using this model, we identify the underlying issues and the necessary changes
to improve it.
Based on these insight, we formally define AL's syntax and semantics to
accurately capture Wasm control flow.
We then implement an AL interpreter according to the formal definition and
evaluate its correctness.
The interpreter successfully passes all tests in the Wasm official test suite,
as well as tests from proposals.

% Contribution
The contributions of this paper are as follows:
\begin{itemize}
  \item We propose a formal model for Wasm control flow. (\cref{sec:model})
  \item We define syntax and semantics of AL (\cref{sec:definition})
  \item We implement an AL interpreter for executable specification
    (\cref{sec:exec-spec})
\end{itemize}

>>>>

% Solution
To address this, we present a formal model for how the prose specification
describes Wasm semantics.
Using this model, we identify the underlying issues and the necessary changes
to improve it.
Based on these insight, we formally define AL's syntax and semantics to
accurately capture Wasm semantics.
We then implement an AL interpreter according to the formal definition and
evaluate its correctness.
The interpreter successfully passes all tests in the Wasm official test suite,
as well as tests from proposals.

% Contribution
The contributions of this paper are as follows:
\begin{itemize}
  \item We propose a formal model for the prose specification.
    (\cref{sec:model})
  \item We define syntax and semantics of AL (\cref{sec:definition})
  \item We implement an AL interpreter for executable specification
    (\cref{sec:exec-spec})
\end{itemize}
